---
title: "airquality_vignette"
author: "Lucas Rosenbusch"
date: "5/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
```

Welcome to the **airquality** package. This package uses various data from the [\textcolor{blue}{OpenWeatherMap API}](https://openweathermap.org/api).

It includes various functions that help you to get an overview about the airquality in any town. You can:

-   retrieve the current airquality index and airquality subcomponents
-   plot the airquality index and concentration of air quality components for the past two weeks
-   retrieve and compare the airquality index of the ten biggest European cities
-   get the current weather data

In the following, each function is explained in detail and examples are provided.

# How to install the airquality package
```{r warning = FALSE}
library(airquality)
```

\newpage

# Current Airquality Data (data frame)
This function takes the city and country (use ISO 3166 country codes) of interest as arguments. It outputs a data frame containing the: 

* Air Quality Index (AQI) 
  + the aqi ranges from 1 = good to 5 = very Poor 
* Carbon monoxide concentration (CO) 
* Nitrogen monoxide concentration (NO) 
* Nitrogen dioxide concentration (NO2)
* Ozone concentration (O3) 
* Sulphur dioxide concentration (SO2) 
* Particulates concentration (PM2_5 and PM_10) 
* Ammonia concentration (NH3)
```{r warning = FALSE}
library(airquality)
current_aq_df("Amsterdam", "NL")
```

To display the output to users in a nicer way, you can use the gt::gt() function 
```{r}
library(gt)
gt(current_aq_df())
```
